Bayesian Inference Using Sequential Monte-Carlo Algorithm for Dynamic System Models

### 2020-08-18 appendix/appendix.tex
Fig fix
Big fix

\begin{table}[H]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment        & Version                \\ [0.5ex]
        \hline\hline
        Operating system   & macOS Catalina 10.15.6 \\
        PyCharm (IDE)      & Professional 202.2     \\
        Python interpretor & 3.7.0                  \\
        IPython            & 7.12.0                 \\
        Clang              & 6.0 (clang-600.0.57)   \\
        \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

Version requirements for some critical site packages (\verb|Python|) used in the code are listed in Table \ref{table:local_package}.

\begin{table}
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment & Version         \\ [0.5ex]
        \hline\hline
        pyABC       & $\simeq$ 0.10.3 \\
        NumPy       & $\simeq$ 1.18.4 \\
        SciPy       & $\simeq$ 1.4.1  \\
        pandas      & $\simeq$ 1.1.0  \\
        matplotlib  & $\simeq$ 3.0.1  \\
        bokeh       & $=$ 1.4.0       \\
        \hline
    \end{tabular}
    \caption{Site packages on local machine}
    \label{table:local_package}
\end{table}

Local development and some runs of small size were done under the hardware listed in Table \ref{table:local_hardware}. When running ABC SMC, the program can make used of 8 python process (Hyper-Threading enabled) and run under 3.8GHz (maximal) for a long time under proper cooling, proved that the program could efficiently use the computation resources for a local personal computer. It is noted that the program took no advantage of graphics card, as \verb|multiprocessing| along can only exploit the resources inside CPU. The execution time and other performance data presented in Chapter 5 were obtained using remote machines but not local machine.

@@

Cirrus hardware can be found in \url{https://www.cirrus.ac.uk/about/hardware.html}. The software environment used in the development and experiments are listed in Table \ref{table:cirrus_soft}. Requirement of site packages is the sanme as that on local macine (Table \ref{table:local_package})

@@

\chapter{Data and supplementary figures}

\section{Infer-back experiments}

\subsection{Parameter values used to generate synthetic data}

@@

\subsection{Kernel experiment: median epsilon schedule}

@@

\section{Parameter inference and model comparison results}

    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/resultCurve_uni.png}}
    \end{center}

    \caption{Simulated data from the last population of model 1, 2 and 3, using uniform prior.  Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small)}
    \label{fig:resultCurve_uni}

\begin{figure}[ht]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/inferno5.png}}
    \end{center}
    \caption[Joint density distribution of each parameter pair]%
    {Joint distribution of each parameter pair. The diagonal is KDE fit of each individual parameter, the upper triangle contains scatter plot of the particles and the lower triangle is the joint density distribution for each parameter pair}
    \label{fig:model5_para_joint}
\end{figure}

\begin{figure}[ht]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/credible.png}}
    \end{center}
    \caption[Credible intervals of parameters in model 5]%
    {Credible intervals of parameters in model 5 across all generations}
    \label{fig:credible}
\end{figure}

>>>>

\begin{table}[H]
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment        & Version                \\ [0.5ex]
        \hline\hline
        Operating system   & macOS Catalina 10.15.6 \\
        PyCharm (IDE)      & Professional 2020.2    \\
        Python interpretor & 3.7.0                  \\
        IPython            & 7.12.0                 \\
        Clang              & 6.0 (clang-600.0.57)   \\
        \hline
    \end{tabular}
    \caption{Environment on local machine}
    \label{table:local_macine}
\end{table}

Version requirements for some critical site packages (\verb|Python|) used in the code are listed in Table \ref{table:local_package}. When replicating the experiments, higher version of these packages are acceptable, except \verb|bokeh|.

\begin{table}
    \centering
    \begin{tabular}{|c c|}
        \hline
        Environment & Version \\ [0.5ex]
        \hline\hline
        pyABC       & 0.10.3  \\
        NumPy       & 1.18.4  \\
        SciPy       & 1.4.1   \\
        pandas      & 1.1.0   \\
        matplotlib  & 3.0.1   \\
        bokeh       & 1.4.0   \\
        \hline
    \end{tabular}
    \caption{Site packages on local machine}
    \label{table:local_package}
\end{table}

Local development and some runs of small size were done under the hardware listed in Table \ref{table:local_hardware}. When running ABC SMC, the program can make used of 8 python process (Hyper-Threading enabled) and run under 3.8GHz (maximal) for a long time under proper cooling, proved that the program could efficiently use the computation resources for a local personal computer. The execution time and other performance data presented in Chapter 5 were obtained using remote machines but not local machine.

@@

Most experiments were performaed on Cirrus, its hardware can be found in Table \ref{table:remote_hardware}. The program can run in sigle compute-node which contains two processors\footnote{\url{https://www.cirrus.ac.uk/about/hardware.html}}. The software environment used in the development and experiments are listed in Table \ref{table:cirrus_soft}. Requirement of site packages is the same as that on local macine (Table \ref{table:local_package})

\begin{table}
    \centering
    \begin{tabular}{|c c|}
        \hline
        Hardware        & Detail                                          \\ [0.5ex]
        \hline\hline
        Processors      & 2.1 GHz, 18-core Intel Xeon E5-2695 (Broadwell) \\
        Architecture    & x86-64                                          \\
        Hyper-Threading & Supported                                       \\
        Memory          & 256 GB NUMA, shared between two processors         \\
        \hline
    \end{tabular}
    \caption{Cirrus hardware (compute node)}
    \label{table:remote_hardware}
\end{table}

@@

\chapter{Supplementary figures and data}

% \section{Infer-back experiments}

% \subsection{Parameter values used to generate synthetic data}

@@

% \subsection{Kernel experiment: median epsilon schedule}

@@

% \section{Parameter inference and model comparison results}

\begin{figure}[H]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/credible.png}}
    \end{center}
    \caption[Credible intervals of parameters in model 5]%
    {Credible intervals of parameters in model 5 across all generations}
    \label{fig:credible}
\end{figure}

### 2020-08-18 conclusion/conclusion.tex
Big fix

 The inference program was mostly run on multi-core machines, and additional scaling-up performance test illustrated the scaling behaviour. When the number of running \verb|Python| process exceeds the number of physical cores, hyperthreading would be enabled, and performance improvement was still considerable (Figure \ref{fig:sample_per_sec}). Studies on the variant required samples revealed that some threshold paths could lead to local optimum and significantly affect the efficiency. A non-linear relationship between the required samples and execution time was also observed in the first two generations.

@@

 From this application, some suggestions on ABC SMC implementation could be drawn. How to set the prior could be the most tricky decision for high dimensional parameter inference. The distribution and the interval of each parameter can affect the inference results significantly, and improper prior cold lead to poor fit. In our cases, log-uniform prior gave better fits than uniform prior. The threshold path and plot of required samples in each generation can be used to identify possible local modes; if stuck, it takes much more samples than usual to move out. To avoid this, large population size and a proper epsilon schedule may help. For the uncertainties observed in model selection and some duplicated runs with high variance, a longer run with more generation could help to identify whether the convergency is consistent such that a reproducible inferred results can be obtained.

@@

>>>>

 The inference program was mostly run on multi-core machines, and additional scaling-up performance test illustrated the scaling behaviour.

 When the number of running \verb|Python| processes is less than the number of physical cores, a considerable scaling performance was observed. Studies on the variant required sample numbers revealed that some threshold paths could lead to local optimum and significantly affect the efficiency. A non-linear relationship between the required sample numbers and required execution time was also observed and made the detailed analysis complicated.

@@

 From this application, some suggestions on ABC SMC implementation could be drawn.The prior distribution and interval of each parameter can affect the inference results significantly, and improper prior cold lead to poor fit. In our cases, log-uniform prior gave better fits than uniform prior. The threshold path and plot of required samples in each generation can be used to identify possible local modes; if stuck, it takes much more samples than usual to move out. To avoid this, large population size and a proper epsilon schedule may help. For the uncertainties observed in model selection and some duplicated runs with high variance, a longer run with more generation could help to identify whether the convergency is consistent such that a reproducible inferred results can be obtained.

@@

In terms of the project progress regarding original project proposal, all the proposed subjects were explicitly studied as planned. We found that code development cost less time than expected, however, implementations and debugging cost more efforts than expected because of both uncertainties in both the inference ability of the algorithm for our problem, and the implementation options and algorithm hyperparameters. Further on our results, we studied some in-depth topics and derived more conclusions. Some interesting further topics were found in the studies, e.g. comparison with other algorithms and implementation optimisations, however, they were not conducted due the insufficient time.

Also, we found that risk analysis and management throughout the project were helpful. Thanks to the planned mitigations and backup strategies, we were able to proceed with our project as planned when interruptions happened. We experienced local laptop broken and unavailability of remote machines, which consequently made our development and implementations harder. We were able to proceed with the project by using backup plans for local development and using Cirrus or ARCHER interchangeably during their downtime.

### 2020-08-18 implementation/implementation.tex
Big fix

    \caption[Total required samples of different kernels]%
    {Total required samples of different kernels after 20 populations (2000 particles in each population). Different color represents different generations (bottom to top: population 1 to population 20)}
    \label{fig:kernel1}

@@

Two types of factor and adaptive distance function were tested by running the same number of generations (20 generations, 2000 particles per generation). The first type of factor is 25:75  factor, where the first half of the trajectory data were assigned higher factor (75), and the second half of the data was assigned lower factor (25); this could make the first half of the data more `important' in the inference. The second factor was `range' factor, which tried to normalise the trajectory of each dependent variable according to its data range.

From Figure \ref{fig:factor}, different types of factor gave different performance. 25:75 factor required much more samples in the first generation (orange bar in the left of Figure \ref{fig:factor}) and also did not improve much in later generations; thus, it is the slowest one. The first half of observed data contained more features and information, assigning it with higher factor would make the algorithm think that it is more important to fit the first half and thus focus on the hard part, and consequently more particles were needed in the inference process. The acceptance rates of 25:75 factor among different generations were also generally slightly lower than the standard. By contrast, range factor required less total samples and gave generally higher acceptance rates than standard, which made it considerably faster. The adaptive distance gave the best efficiency, as it significantly improved the acceptance rates and resulted in even less required samples (right, Figure \ref{fig:factor}).

@@

    \caption[Factors and adaptive distance experiments]%
    {Factors and adaptive distance experiments. Left: total required samples. Different color represents different generations (bottom totop: population 1 to population 20). Right: acceptance rates in each generation. }
    \label{fig:factor}

@@

    \caption[Simulated trajectories ]%
    {Simulated trajectories from the last population in the factor and adaptive distance experiment. 500 randomly chosen particles from last population are used to generate a sequence of trajectories where mean and inter-quartile range are calculated from. 25:75 factor showed very similar curve as the range factor.  
    }
    \label{fig:factor_sim}

@@

    \caption[Data size and prior distribution range experiment]%
    {Data size and prior distribution range experiment. Left: total required samples. Right: epsilon values under median epsilon schedule}
    \label{fig:size}

@@

This subsection aims to explore options in ABC SMC implementations preliminarily. From the above results, we adopted multivariate normal kernel as the kernel for our real inference on observed data; Local M-NN kernels were also planned to be tested. In the real inference, 25:75 factor were also tried to see if it could help in recovering more features and resulting in a better fit. Because the improvement by using less data was inapparent, we did not try to change the target summary data size. Prior intervals were explored explicitly and gradually shrunk for our models.

@@

Two prior intervals ([0, 25] and [0, 75]) and two distribution shape (uniform and log-uniform) were tried in the parameter estimation of the first three models. All these ABC SMC runs used 2,000 particles per population and 30 generations.

@@

The resultant simulated data from model 2 and 3 have similar trends, while the most obvious difference is that for model 3, the simulated data of $\Phi$ and $\alpha$ are more `flat'. We expected model 3 to be the best as it reached a lower threshold value, and intuitively gives a better fit. However, the fit of all these models could not be considered as a generally good representation of the biological process that we want to approximate: for tnf-$\alpha$, the simulated data were significantly biased from the observed data. A sharp peak at 4 hpl was observed in the experimental data, but none of the three models represents similar features.

@@

    \caption[Estimated posterior distribution of parameters in model 3]%
    {Estimated posterior distribution of parameters in model 3. Shaded range indicates 25\%--75\% quantile of the population}
    \label{fig:para1}

@@

Compared to uniform-distributed prior, we found that log-uniform distributed prior is more suitable in our parameter inference. Log-uniform resulted in an obviously better fit and narrower inter-quantile interval (Figure \ref{fig:result123} and \ref{fig:resultCurve_uni}), and the final epsilon value was also smaller. Log-uniform tends to assign values that are close to the left boundary (i.e. zero in our case) with higher density, i.e. they are more likely to be sampled in the first population. As a result, the parameter estimates are expected to have smaller mean values or skewed to the left of the x-axis. The estimated values proved this ( \ref{table:estimated1}). This was also observed in other models and prior interval experiments. It indicated that some of the parameters tend to have small true values that are close to zero, and using log-uniform prior could result in a faster and more satisfying inference. Regarding this, further experiments all used log-uniform prior only.

@@

We observed that the existing models could not well represent the trajectory of relative expression of tnf-$\alpha$. From experimental data, a rapid increase of tnf-$\alpha$ expression was observed in 0--4 hpl, followed by a rapid drop. All the models cannot well recover this feature, and most results saw a less-rapid increase followed by a gradual decrease, while the observed peak value was not reached (Figure \ref{fig:result123}). Also, in some other case, e.g. uniform runs (Figure \ref{fig:resultCurve_uni}), tnf-$\alpha$ trajectories was well fitted; however, at the cost of under-fitting $\Phi$ curve. Hence efforts had been spent to propose more alternative models that can potentially solve this problem.

@@

    \caption[Simulated trajectory from the 30th population of model 5, with 25:75 factor applied]{Simulated trajectory from the 30th population of model 5, with 25:75 factor applied. Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small).}
    \label{fig:overfit}
\end{figure}

@@

Model 4 did not overweight other models across all the generations; model 3 gained an advantage before generation 15 except generation 5. After generation 18 ($\epsilon_{18} = 16.98$), model 5 gained absolute advantage and won in further generations. Also, repeated runs showed similar trends: although uncertainties (e.g. violently changes mode probabilities) were present before generation 20, model 5 won with nearly 100\% probability in later generations where epsilon values were considerably low, i.e. $\epsilon_t<16$.

Based on the model comparison results, we could conclude that model 5 was the best model among the tested models. Uncertainties were observed in early generations, where similar patterns were also observed in the model comparison of model 1, 2 and 3. We considered the violently changing model probability in early generations is related to the inference ability at high epsilon threshold values (epsilon) and possibly the insufficient exploration of the parameter space. However as we only focused on the best model with small final threshold $\epsilon_T$, the easiest way is to extend the number of generation until epsilon converges, or increase the population size for a more statistically confident probability.

@@

For the best model (model 5), the inferred parameter posterior distribution of model 5 is shown in Figure \ref{fig:model5_para}, the estimated mean values is shown in Table \ref{table:estimated5}. The pair-wise joint density distribution is shown in Figure \ref{fig:model5_para_joint}. Most of the inferred posteriors show a bell-shaped density distribution, indicating that they are Gaussian distributed. A thin and concentrated shape indicates a well-inferred parameter, e.g. $\mu{\Phi}$ and $\kappa_{\Phi\beta}$. Some distributions, however, are skewed to zero, e.g. $\mu_N$ and $s_{\alpha\Phi}$.

By looking at the joint density plot (Figure \ref{fig:model5_para_joint}), some correlated patterns are observed. For example, an obvious linear relationship on the distributions of $\mu_\beta$ and $s_{\beta\Phi}$. This leads us to consider that reducing the number of parameters in the model is possible. Highly correlated parameters can be reduced, e.g. $s_{\beta\Phi}$ can be expressed as $A\mu_\beta+B$ where $A$ and $B$ can be calculated from the joint distribution by fitting a linear regression.

@@

    \caption[Inferred posterior distribution of parameters in model 5]%
    {Inferred posterior distribution of parameters in model 5. Shaded range indicates 25\%--75\% quantile of the population}
    \label{fig:model5_para}

@@

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/pc.png}}
    \end{center}

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{0.8\hsize}{!}{\includegraphics{fig/pc_pie.png}}
    \end{center}

@@

>>>>

    \caption[Total required number of sample for different kernels]%
    {Total required samples of different kernels after 20 populations (2000 particles in each population). Different color represents different generations (bottom to top: population 1 to population 20)}
    \label{fig:kernel1}

@@

Two types of factor and adaptive distance function were tested by running the same number of generations (20 generations, 2000 particles per generation). The first type of factor is 75:25 factor, where the first half of the trajectory data were assigned higher factor (75), and the second half of the data was assigned lower factor (25); this could make the first half of the data more `important' in the inference. The second factor was `range' factor, which tried to normalise the trajectory of each dependent variable according to its data range.

From Figure \ref{fig:factor}, different types of factor gave different performance. 75:25 factor required much more samples in the first generation (orange bar in the left of Figure \ref{fig:factor}) and also did not improve much in later generations; thus, it is the slowest one. The first half of observed data contained more features and information, assigning it with higher factor would make the algorithm think that it is more important to fit the first half and thus focus on the hard part, and consequently more particles were needed in the inference process. The acceptance rates of 75:25 factor among different generations were also generally slightly lower than the standard. By contrast, range factor required less total samples and gave generally higher acceptance rates than standard, which made it considerably faster. The adaptive distance gave the best efficiency, as it significantly improved the acceptance rates and resulted in even less required samples (right, Figure \ref{fig:factor}).

@@

    \caption[Factors and adaptive distance experiments]%
    {Factors and adaptive distance experiments. Left: total required number of samples. Different color represents different generations (bottom to top: population 1 to population 20). Right: acceptance rates in each generation. }
    \label{fig:factor}

@@

    \caption[Simulated trajectories ]%
    {Simulated trajectories from the last population in the factor and adaptive distance experiment. 500 randomly chosen particles from last population are used to generate a sequence of trajectories where mean and inter-quartile range are calculated from. 75:25 factor showed very similar curve as the range factor.  
    }
    \label{fig:factor_sim}

@@

    \caption[Data size and prior distribution range experiment]%
    {Data size and prior distribution range experiment. Left: total required number of samples. Right: epsilon values under median epsilon schedule}
    \label{fig:size}

@@

This section aims to explore options in ABC SMC implementations preliminarily. From the above results, we adopted multivariate normal kernel as the kernel for our real inference on observed data; Local M-NN kernels were also planned to be tested. In the real inference, 75:25 factor were also tried to see if it could help in recovering more features and resulting in a better fit. Prior intervals were explored explicitly and gradually shrunk for our models.

% Because the improvement by using less data was inapparent, we did not try to change the target summary data size.

@@

Two prior intervals ([0, 25] and [0, 75]) and two distribution shape (uniform and log-uniform) were tried in the parameter estimation of the first three models. All these ABC SMC runs used 2,000 particles per population and 30 generations. The population size should be set at a high level (e.g. $\geq 1000$ in our case) when having models with many parameters to ensure a statistically adequate exploration. The convergency were usually observed around generation 20 in our previous experiments; the length of generation is set to 30 to ensure that most runs converge in the end.

@@

The resultant simulated data from model 2 and 3 have similar trends, while the most obvious difference is that for model 3, the simulated data of $\Phi$ and $\alpha$ are more `flat'. We expected model 3 to be the best as it reached a lower threshold value, and intuitively gives a better fit. However, the fit of all these models could not be considered as a generally good representation of the biological process that we want to approximate: for tnf-$\alpha$, the simulated data and the observed data show largely different trends. A sharp peak at 4 hpl was observed in the experimental data, but none of the three models represents similar features (Figure \ref{fig:result123}).

@@

    \caption[Estimated posterior distribution of parameters in model 3]%
    {Estimated posterior distribution of parameters in model 3. Shaded range indicates inter-quartile interval}
    \label{fig:para1}

@@

Compared to uniform-distributed prior, we found that log-uniform distributed prior is more suitable in our parameter inference. Log-uniform resulted in an obviously better fit and narrower inter-quantile interval (Figure \ref{fig:result123} and \ref{fig:resultCurve_uni}), and the final epsilon value was also smaller. Log-uniform tends to assign values that are close to the left boundary (i.e. zero in our case) with higher density. As a result, the parameter estimates from log-uniform prior are highly likely to have smaller mean values than that from uniform prior, and the inferred parameter values proved this (Table \ref{table:estimated1}). This was also observed in other models and prior interval experiments. It indicated that some of the parameters tend to have small true values that are close to zero, and using log-uniform prior could result in a faster and more satisfying inference. Regarding this, further experiments all used log-uniform prior only.

@@

We observed that the existing models could not well represent the trajectory of relative expression of tnf-$\alpha$. From experimental data, a rapid increase of tnf-$\alpha$ expression was observed in 0--4 hpl, followed by a rapid drop. All the models cannot well recover this feature, and most results saw a less-rapid increase followed by a gradual decrease, while the observed peak value was not reached (Figure \ref{fig:result123}).

Also, in some other experiment results, e.g. uniform runs (Figure \ref{fig:resultCurve_uni}), tnf-$\alpha$ trajectories was well fitted; however, at the cost of under-fitting $\Phi$ curve. Hence efforts had been spent to propose more alternative models that can potentially solve this problem.

\begin{figure}[h]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/resultCurve_uni.png}}
    \end{center}

    \caption[Simulated data from the last population of model 1, 2 and 3, using uniform prior]{Simulated data from the last population of model 1, 2 and 3, using uniform prior.  Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small)}
    \label{fig:resultCurve_uni}
\end{figure}

@@

    \caption[Simulated trajectory from the 30th population of model 5, with 75:25 factor applied]{Simulated trajectory from the 30th population of model 5, with 75:25 factor applied. Error bar indicates SEM (for $N$ and $\Phi$ the SEM is relatively small).}
    \label{fig:overfit}
\end{figure}

@@

From the model probability plot (Figure \ref{fig:model345cmp}), we found that model 4 did not overweight other models across all the generations. Model 3 was comitative and gained advantages at most early generation. From generation 14 and onwards, model 5 saw a gradually increasing probability and gained 100\% model probability after generation 18 ($\epsilon_{18} = 16.98$) and won in further generations. Also, repeated runs showed similar trends, although uncertainties (e.g. drastically model probability changes) were present before generation 20, model 5 won with nearly 100\% probability in later generations where epsilon values were considerably low, i.e. $\epsilon_t<16$.

Based on the model comparison results, we could conclude that model 5 was the best model among the tested models. Uncertainties were observed in early generations, where similar patterns were also observed in the model comparison of model 1, 2 and 3. We considered the drastically changing model probability in early generations is related to the inference ability at high epsilon threshold values (epsilon) and possibly the insufficient exploration of the parameter space. However as we only focused on the best model with small final threshold $\epsilon_T$, the easiest way is to extend the number of generation until epsilon converges, or increase the population size for a more statistically confident probability.

@@

For the best model (model 5), the inferred parameter posterior distribution of model 5 is shown in Figure \ref{fig:model5_para}, the estimated mean values is shown in Table \ref{table:estimated5}. The pair-wise joint density distribution is shown in Figure \ref{fig:model5_para_joint}. Most of the inferred posteriors show a bell-shaped density distribution with a single peak.. A thin and concentrated shape indicates a well-inferred parameter, e.g. $\mu{\Phi}$ and $\kappa_{\Phi\beta}$. Some distributions, however, are skewed to zero, e.g. $\mu_N$ and $s_{\alpha\Phi}$. Concentrations in the posteriors were presented, and using inter-quartiles (shaded interval in Figure \ref{fig:model5_para}) or mean values to summarise the posteriors is feasible in practice uses, e.g. simulating data (Figure \ref{fig:overfit}).

By looking at the joint density plot (Figure \ref{fig:model5_para_joint}), some correlated patterns are observed. For example, an obvious linear relationship is presented in the joint distribution of $\mu_\beta$ and $s_{\beta\Phi}$. This leads us to consider that we could possibly reduce the number of parameters, e.g. replace $s_{\beta\Phi}$ by $A\mu_\beta+B$ where $A$ and $B$ can be calculated from the joint distribution by fitting a linear regression. The reason for the highly correlated pattern, or `fat' distribution shapes could be that the provided data are lees informative about the parameters.

@@

    \caption[Inferred posterior distribution of parameters in model 5]%
    {Inferred posterior distribution of parameters in model 5. Shaded range indicates inter-quartile  interval of the population}
    \label{fig:model5_para}

@@

\begin{figure}[h]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/inferno5.png}}
    \end{center}
    \caption[Joint density distribution of each parameter pair]%
    {Joint distribution of each parameter pair. The diagonal is KDE fit of each individual parameter, the upper triangle contains scatter plot of the particles and the lower triangle is the joint density distribution for each parameter pair}
    \label{fig:model5_para_joint}
\end{figure}

@@

\begin{figure}[H]
    \begin{center}
        \resizebox{1.0\hsize}{!}{\includegraphics{fig/pc.png}}
    \end{center}

@@

\begin{figure}[ht!]
    \begin{center}
        \resizebox{0.7\hsize}{!}{\includegraphics{fig/pc_pie.png}}
    \end{center}

@@

To conclude, model 5 is most sensitive to the parameters in the equations for cells' dynamics (i.e. first two equations in Eqn.\ref{eq:model5}), especially to $a$ and $\mu_\Phi$.
